---
title: "Alpha"
output:
  word_document: default
  html_document: default
date: "2022-08-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.asp=0.8)
```

```{r}
library(tidyverse)
library(psych)
library(feather)
source("funcs.R")
```

## SOCS-S

```{r}
df <- read_feather("../results/tidy_filtered_responses.feather") %>% 
  filter(str_starts(item, "SOCS_S")) %>% 
  remove_nas() %>% 
  mutate(response = as.double(response))

df
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

## SOCS-O

```{r}
df <- read_feather("../results/tidy_filtered_responses.feather") %>% 
  filter(str_starts(item, "SOCS_O")) %>% 
  remove_nas() %>% 
  mutate(response = as.double(response))

df
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

## CEAS-FROM

```{r}
df <- remove_nas(read_feather("../results/tidy_ceas_from.feather"))
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

```{r}
get_alpha(df)
```

### CEAS_FROM_Engagement

```{r}
get_alpha(filter(df, sub_scale == "CEAS_FROM_Engagement"))
```

### CEAS_FROM_Action

```{r}
get_alpha(filter(df, sub_scale == "CEAS_FROM_Action"))
```

## CEAS-SC

```{r}
df <- remove_nas(read_feather("../results/tidy_ceas_sc.feather"))
get_alpha(df)
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

### CEAS_S\_Action

```{r}
get_alpha(filter(df, sub_scale == "CEAS_S_Action"))
```

### CEAS_S\_Engagement_Dimension_1

```{r}
get_alpha(filter(df, sub_scale == "CEAS_S_Engagement_Dimension_1"))
```

### CEAS_S\_Engagement_Dimension_2

```{r}
get_alpha(filter(df, sub_scale == "CEAS_S_Engagement_Dimension_2"))
```

## CEAS-TO

```{r}
df <- remove_nas(read_feather("../results/tidy_ceas_to.feather"))
get_alpha(df)
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

### CEAS_TO_Action

```{r}
get_alpha(filter(df, sub_scale == "CEAS_TO_Action"))
```

### CEAS_TO_Engagement

```{r}
get_alpha(filter(df, sub_scale == "CEAS_TO_Engagement"))
```

## CS

```{r}
df <- remove_nas(read_feather("../results/tidy_cs.feather"))
get_alpha(df)
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

### CS_Common_Humanity

```{r}
get_alpha(filter(df, sub_scale == "CS_Common_Humanity"))
```

### CS_Indifference_Reverse

```{r}
get_alpha(filter(df, sub_scale == "CS_Indifference_Reverse"))
```

### CS_Kind

```{r}
get_alpha(filter(df, sub_scale == "CS_Kind"))
```

### CS_Mindfulness

```{r}
get_alpha(filter(df, sub_scale == "CS_Mindfulness"))
```

## DASS-21

```{r}
df <- remove_nas(read_feather("../results/tidy_dass.feather"))
get_alpha(df)
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

### DASS_21_Anxiety

```{r}
get_alpha(filter(df, sub_scale == "DASS_21_Anxiety"))
```

### DASS_21_Depression

```{r}
get_alpha(filter(df, sub_scale == "DASS_21_Depression"))
```

### DASS_21_Somatization

```{r}
get_alpha(filter(df, sub_scale == "DASS_21_Somatization"))
```

## ECR

```{r}
df <- remove_nas(read_feather("../results/tidy_ecr.feather"))
get_alpha(df)
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

## ECR_Anxiety

```{r}
get_alpha(filter(df, sub_scale == "ECR_Anxiety"))
```

## ECR_Avoidance

```{r}
get_alpha(filter(df, sub_scale == "ECR_Avoidance"))
```

## FFMQ

```{r}
df <- remove_nas(read_feather("../results/tidy_ffmq.feather"))
get_alpha(df)
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

### FFMQ_Describe

```{r}
get_alpha(filter(df, sub_scale == "FFMQ_Describe"))
```

### FFMQ_Nonreactivity

```{r}
get_alpha(filter(df, sub_scale == "FFMQ_Nonreactivity"))
```

### FFMQ_Nonjudgement

```{r}
get_alpha(filter(df, sub_scale == "FFMQ_Nonjudgement"))
```

### FFMQ_Nonreactivity

```{r}
get_alpha(filter(df, sub_scale == "FFMQ_Nonreactivity"))
```

### FFMQ_Observe

```{r}
get_alpha(filter(df, sub_scale == "FFMQ_Observe"))
```

## PBIS

```{r}
df <- remove_nas(read_feather("../results/tidy_pbis.feather"))
get_alpha(df)
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

## SCS

```{r}
df <- remove_nas(read_feather("../results/tidy_scs.feather"))

df <- df %>% 
  mutate(response = if_else(scale_valence == "Negative", 6 - response, response))
get_alpha(df)
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

### SCS_Common_Humanity

```{r}
get_alpha(filter(df, sub_scale == "SCS_Common_Humanity"))
```

### SCS_Isolation

```{r}
get_alpha(filter(df, sub_scale == "SCS_Isolation"))
```

### SCS_Mindfulness

```{r}
get_alpha(filter(df, sub_scale == "SCS_Mindfulness"))
```

### SCS_Overidentification

```{r}
get_alpha(filter(df, sub_scale == "SCS_Overidentification"))
```

### SCS_Self_Judgement

```{r}
get_alpha(filter(df, sub_scale == "SCS_Self_Judgement"))
```

### SCS_Self_Kindness

```{r}
get_alpha(filter(df, sub_scale == "SCS_Self_Kindness"))
```

## WEMWBS

```{r}
df <- remove_nas(read_feather("../results/tidy_wemwbs.feather"))
get_alpha(df)
```

```{r fig.asp = 0.8, fig.width = 7}
plot_response_distribution(df)
```

```{r}
sessionInfo()
```
