---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggthemes)
library(feather)
library(lubridate)
library(jtools)
```

```{r}
df <- read_csv("../data/Compassion_14 November 2021_16.36.csv")
df
```

```{r}
df <- df %>% 
  slice(3:n()) %>% 
  mutate(StartDate = as.Date(StartDate)) %>% 
  filter(StartDate >= ymd("2021-01-02"))
```

```{r}
responses <- df %>% 
  select(
    ResponseId,
    starts_with("SOCS")
)

responses
```

```{r}
ordered_responses <- responses %>% 
  mutate(across(starts_with("SOCS"), ~if_else(is.na(.), ., str_extract(., "\\d$")))) %>% 
  pivot_longer(starts_with("SOCS"), names_to = "item", values_to = "response") %>% 
  mutate(response = ordered(response, levels = c("1", "2", "3", "4", "5")))

ordered_responses
```

```{r}
ordered_responses %>% 
  write_feather("../results/tidy_responses.feather")
```

```{r, fig.width=16, fig.height=9}
ggplot(ordered_responses, aes(x=response)) +
  geom_bar(stat = "count") +
  facet_wrap(~item, ncol = 10) +
  theme_apa()
```

Looks like very few people fell for SOCS-O 5 (The attention check.) I'm
going to remove this item and and anyone who didn't respond to it.

```{r}
filtered_responses <- responses %>%
  mutate(across(-ResponseId, ~if_else(is.na(.), ., str_extract(., "\\d+$")))) %>% 
  filter(`SOCS-O_5` == "5") %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>% 
  mutate(response = ordered(response, levels = c("1", "2", "3", "4", "5"))) %>% 
  filter(item != "SOCS-O_5") %>% 
  mutate(item_number = if_else(as.numeric(str_extract(item, "\\d+")) > 5 & str_detect(item, "SOCS-O"), as.numeric(str_extract(item, "\\d+")) - 1, as.numeric(str_extract(item, "\\d+")))) %>% 
  mutate(item = if_else(str_detect(item, "SOCS-O"), str_c("SOCS-O_", item_number), item)) %>% 
  select(-item_number) %>% 
  mutate(sub_scale = case_when(
    item %in% c("SOCS-S_1", "SOCS-S_6", "SOCS-S_11", "SOCS-S_16") ~ "SOCS_S_Recognizing_Suffering",
    item %in% c("SOCS-S_2", "SOCS-S_7", "SOCS-S_12", "SOCS-S_17") ~ "SOCS_S_Understanding_Suffering",
    item %in% c("SOCS-S_3", "SOCS-S_8", "SOCS-S_13", "SOCS-S_18") ~ "SOCS_S_Feeling_Suffering",
    item %in% c("SOCS-S_4", "SOCS-S_9", "SOCS-S_14", "SOCS-S_19") ~ "SOCS_S_Tolerating_Feelings",
    item %in% c("SOCS-S_5", "SOCS-S_10", "SOCS-S_15", "SOCS-S_20") ~ "SOCS_S_Acting_To_Alleviate",
    item %in% c("SOCS-O_1", "SOCS-O_6", "SOCS-O_11", "SOCS-O_16") ~ "SOCS_O_Recognizing_Suffering",
    item %in% c("SOCS-O_2", "SOCS-O_7", "SOCS-O_12", "SOCS-O_17") ~ "SOCS_O_Understanding_Suffering",
    item %in% c("SOCS-O_3", "SOCS-O_8", "SOCS-O_13", "SOCS-O_18") ~ "SOCS_O_Feeling_Suffering",
    item %in% c("SOCS-O_4", "SOCS-O_9", "SOCS-O_14", "SOCS-O_19") ~ "SOCS_O_Tolerating_Feelings",
    item %in% c("SOCS-O_5", "SOCS-O_10", "SOCS-O_15", "SOCS-O_20") ~ "SOCS_O_Acting_To_Alleviate"
  ))
```

```{r, fig.width=16, fig.height=9}
ggplot(filtered_responses, aes(x=response)) +
  geom_bar(stat = "count") +
  facet_wrap(~item, ncol = 10) +
  theme_apa()
```

```{r}
filtered_responses %>% 
  write_feather("../results/tidy_filtered_responses.feather")
```

```{r}
demographics <- df %>% 
  select(ResponseId, starts_with("DEM")) %>% 
  pivot_longer(-ResponseId, names_to = "dem_item", values_to = "dem_value", values_drop_na=TRUE)

demographics
```

```{r}
demographics %>% 
  write_feather("../results/tidy_demographics.feather")
```

```{r}
socs_sub_scales <- filtered_responses %>% 
  mutate(scale_type = str_extract(item, "SOCS-[A-Z]")) %>% 
  mutate(response = as.numeric(response)) %>% 
  group_by(ResponseId, sub_scale) %>% 
  summarise(socs_subscale_total = sum(response)) %>% 
  pivot_wider(ResponseId, names_from = sub_scale, values_from = socs_subscale_total)

socs_scales <- filtered_responses %>%
  mutate(scale_type = str_extract(item, "SOCS-[A-Z]")) %>% 
  mutate(response = as.numeric(response)) %>% 
  group_by(ResponseId, scale_type) %>% 
  summarise(socs_total = sum(response)) %>% 
  pivot_wider(ResponseId, names_from = scale_type, values_from = socs_total) %>% 
  inner_join(socs_sub_scales)

socs_scales
```

```{r}
socs_scales %>% 
  write_feather("../results/socs_scales.feather")
```

### PBIS

```{r}
tidy_pbis <- df %>% 
  semi_join(socs_scales) %>% 
  select(ResponseId, starts_with("PBIS")) %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>% 
  mutate(response = as.numeric(str_extract(response, "\\d$")))

tidy_pbis
```

```{r}
tidy_pbis %>% 
  write_feather("../results/tidy_pbis.feather")
```

```{r}
pbis_scales <- tidy_pbis %>% 
  group_by(ResponseId) %>% 
  summarise(PBIS = mean(response))

pbis_scales
```

```{r}
pbis_scales %>% 
  write_feather("../results/pbis_scales.feather")
```

### CS

```{r}
tidy_cs <- df %>% 
  semi_join(socs_scales) %>% 
  select(ResponseId, starts_with("CS")) %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>% 
  mutate(response = as.numeric(str_extract(response, "\\d$"))) %>% 
  mutate(
    response=if_else(
      item %in% c("CS_3", "CS_7", "CS_11", "CS_15"),  # Indifference subscales are reverse coded
      case_when(response == 5 ~ 1,
                response == 4 ~ 2,
                response == 2 ~ 4,
                response == 1 ~ 5,
                TRUE ~ response),
                 response)) %>% 
  mutate(sub_scale = case_when(
    item %in% c("CS_2", "CS_6", "CS_10", "CS_14") ~ "CS_Kind",
    item %in% c("CS_1", "CS_5", "CS_9", "CS_13") ~ "CS_Mindfulness",
    item %in% c("CS_3", "CS_7", "CS_11", "CS_15") ~ "CS_Indifference_Reverse",
    item %in% c("CS_4", "CS_8", "CS_12", "CS_16") ~ "CS_Common_Humanity",
  ))

tidy_cs
```

```{r}
tidy_cs %>% 
  write_feather("../results/tidy_cs.feather")
```

```{r}
cs_subscales <- tidy_cs %>% 
  group_by(ResponseId, sub_scale) %>% 
  summarise(sub_scale_response = mean(response)) %>% 
  filter(!is.na(sub_scale_response)) %>% 
  pivot_wider(ResponseId, names_from = sub_scale, values_from = sub_scale_response)

cs_scales <- tidy_cs %>% 
  group_by(ResponseId) %>% 
  summarise(CS_Total = mean(response)) %>% 
  filter(!is.na(CS_Total)) %>% 
  right_join(cs_subscales)
```

```{r}
cs_scales %>% 
  write_feather("../results/cs_scales.feather")
```

### WEMWBS

```{r}
tidy_wemwbs <- df %>% 
  semi_join(socs_scales) %>% 
  select(ResponseId, starts_with("WEMWBS")) %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>% 
  mutate(response = case_when(
    response == "Jamais" ~ 1,
    response == "Rarement" ~ 2,
    response == "Parfois" ~ 3,
    response == "Souvent" ~ 4,
    response == "Tout le temps" ~ 5,
    TRUE ~ NA_real_
  ))

tidy_wemwbs
```

Jamais = Never Rarement = Rarely Parfois = Sometimes Souvent = Often
Tout le temps = All the time

```{r}
tidy_wemwbs %>% 
  write_feather("../results/tidy_wemwbs.feather")
```

```{r}
wemwbs_scales <- tidy_wemwbs %>% 
  group_by(ResponseId) %>% 
  summarise(WEMWBS = sum(response)) %>% 
  filter(!is.na(WEMWBS))

wemwbs_scales
```

```{r}
wemwbs_scales %>% 
  write_feather("../results/wemwbs_scales.feather")
```

### SCS

```{r}
tidy_scs <- df %>% 
  semi_join(socs_scales) %>% 
  select(ResponseId, starts_with("SCS")) %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>% 
  mutate(response = as.numeric(str_extract(response, "\\d$"))) %>% 
    mutate(sub_scale = case_when(
    item %in% c("SCS_5", "SCS_12", "SCS_19", "SCS_23", "SCS_26") ~ "SCS_Self_Kindness",
    item %in% c("SCS_1", "SCS_8", "SCS_11", "SCS_16", "SCS_21") ~ "SCS_Self_Judgement",
    item %in% c("SCS_3", "SCS_7", "SCS_10", "SCS_15") ~ "SCS_Common_Humanity",
    item %in% c("SCS_4", "SCS_13", "SCS_18", "SCS_25") ~ "SCS_Isolation",
    item %in% c("SCS_9", "SCS_14", "SCS_17", "SCS_22") ~ "SCS_Mindfulness",
    item %in% c("SCS_2", "SCS_6", "SCS_20", "SCS_24") ~ "SCS_Overidentification",
  )) %>% 
  mutate(scale_valence = if_else(sub_scale %in% c("SCS_Self_Judgement", "SCS_Overidentification", "SCS_Isolation"), "Negative", "Positive"))

tidy_scs
```

```{r}
tidy_scs %>% 
  write_feather("../results/tidy_scs.feather")
```

```{r}
scs_sub_scales <- tidy_scs %>% 
  group_by(ResponseId, sub_scale) %>%
  summarise(sub_scale_response = mean(response)) %>% 
  filter(!is.na(sub_scale_response)) %>% 
  pivot_wider(ResponseId, names_from = sub_scale, values_from = sub_scale_response)

scs_scales <- tidy_scs %>% 
  group_by(ResponseId, scale_valence) %>% 
  summarise(scale_response = mean(response)) %>% 
  filter(!is.na(scale_response)) %>% 
  pivot_wider(ResponseId, names_from = scale_valence, values_from = scale_response) %>% 
  right_join(scs_sub_scales)

scs_scales
```

```{r}
scs_scales %>% 
  write_feather("../results/scs_scales.feather")
```

### CEAS-SC

```{r}
tidy_ceas_sc <- df %>% 
  semi_join(socs_scales) %>% 
  select(ResponseId, starts_with("CEAS-SC")) %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>% 
  filter(!(item %in% c("CEAS-SC1_3", "CEAS-SC1_7", "CEAS-SC2_3"))) %>% 
  mutate(response = as.numeric(str_extract(response, "\\d+$"))) %>% 
  mutate(sub_scale = case_when(
    item %in% c("CEAS-SC2_1", "CEAS-SC2_2", "CEAS-SC2_4", "CEAS-SC2_5") ~ "CEAS_S_Action",
    item %in% c("CEAS-SC1_2", "CEAS-SC1_4") ~ "CEAS_S_Engagement_Dimension_1",
    item %in% c("CEAS-SC1_1", "CEAS-SC1_5", "CEAS-SC1_6", "CEAS-SC1_8") ~ "CEAS_S_Engagement_Dimension_2",
  )) %>% 
  mutate(item = str_replace(item, "-", "_"))

tidy_ceas_sc
```

```{r}
tidy_ceas_sc %>% 
  write_feather("../results/tidy_ceas_sc.feather")
```

```{r}
ceas_sc_scales <- tidy_ceas_sc %>% 
  group_by(ResponseId, sub_scale) %>% 
  summarise(sub_scale_response = sum(response)) %>% 
  filter(!is.na(sub_scale_response)) %>% 
  pivot_wider(ResponseId, names_from = sub_scale, values_from = sub_scale_response) %>% 
  mutate(CEAS_S_Engagement = CEAS_S_Engagement_Dimension_1 + CEAS_S_Engagement_Dimension_2) %>% 
  mutate(CEAS_S = CEAS_S_Engagement + CEAS_S_Action)

ceas_sc_scales
```

```{r}
ceas_sc_scales %>% 
  write_feather("../results/ceas_sc_scales.feather")
```

### CEAS-TO

Need to filter out attention check. Also removing negative coded items

```{r}
tidy_ceas_to <- df %>% 
  semi_join(socs_scales) %>% 
  select(ResponseId, starts_with("CEAS-TO")) %>% 
  filter(`CEAS-TO1_4` == "Jamais\n1") %>%
  select(-`CEAS-TO1_4`) %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>%
  mutate(item_number = if_else(as.numeric(str_extract(item, "\\d+$")) > 4 & str_detect(item, "CEAS-TO1"), as.numeric(str_extract(item, "\\d+$")) - 1, as.numeric(str_extract(item, "\\d+$")))) %>% 
  mutate(item = if_else(str_detect(item, "CEAS-TO1"), str_c("CEAS-TO1_", item_number), item)) %>% 
  select(-item_number) %>% 
  filter(!(item %in% c("CEAS-TO1_3", "CEAS-TO1_7", "CEAS-TO2_3"))) %>%
  mutate(response = as.numeric(str_extract(response, "\\d+$"))) %>% 
  mutate(sub_scale = case_when(
    str_detect(item, "CEAS-TO1") ~ "CEAS_TO_Engagement",
    str_detect(item, "CEAS-TO2") ~ "CEAS_TO_Action"
  )) %>% 
  mutate(item = str_replace(item, "-", "_"))

tidy_ceas_to
```

```{r}
tidy_ceas_to %>% 
  write_feather("../results/tidy_ceas_to.feather")
```

```{r}
ceas_to_scales <- tidy_ceas_to %>% 
  group_by(ResponseId, sub_scale) %>% 
  summarise(sub_scale_response = sum(response)) %>% 
  filter(!is.na(sub_scale_response)) %>% 
  pivot_wider(ResponseId, names_from = sub_scale, values_from = sub_scale_response) %>% 
  mutate(CEAS_TO = CEAS_TO_Action + CEAS_TO_Engagement)

ceas_to_scales
```

```{r}
ceas_to_scales %>% 
  write_feather("../results/ceas_to_scales.feather")
```

### CEAS-FROM

```{r}
tidy_ceas_from <- df %>% 
  semi_join(ceas_to_scales) %>% 
  select(ResponseId, starts_with("CAES-FROM"), starts_with("CEAS-FROM")) %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>% 
  mutate(item = str_replace(item, "CAES", "CEAS")) %>% 
  mutate(response = as.numeric(str_extract(response, "\\d+$"))) %>%
  filter(!(item %in% c("CEAS-FROM1_3", "CEAS-FROM1_7", "CEAS-FROM2_3"))) %>%
  mutate(sub_scale = case_when(
    str_detect(item, "CEAS-FROM1") ~ "CEAS_FROM_Engagement",
    str_detect(item, "CEAS-FROM2") ~ "CEAS_FROM_Action"
  )) %>% 
  mutate(item = str_replace(item, "-", "_"))


tidy_ceas_from
```

```{r}
tidy_ceas_from %>% 
  write_feather("../results/tidy_ceas_from.feather")
```

```{r}
ceas_from_scales <- tidy_ceas_from %>% 
  group_by(ResponseId, sub_scale) %>% 
  summarise(sub_scale_response = sum(response)) %>% 
  filter(!is.na(sub_scale_response)) %>% 
  pivot_wider(ResponseId, names_from = sub_scale, values_from = sub_scale_response) %>% 
  mutate(CEAS_FROM = CEAS_FROM_Action + CEAS_FROM_Engagement)

ceas_from_scales
```

```{r}
ceas_from_scales %>% 
  write_feather("../results/ceas_from_scales.feather")
```

### FFMQ

```{r}
tidy_ffmq <- df %>% 
  semi_join(ceas_to_scales) %>% 
  select(ResponseId, starts_with("FFMQ")) %>% 
  filter(FFMQ_12 == "Parfois vrai") %>% 
  select(-FFMQ_12) %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>% 
  mutate(item_number = if_else(as.numeric(str_extract(item, "\\d+$")) > 12, as.numeric(str_extract(item, "\\d+$")) - 1, as.numeric(str_extract(item, "\\d+$")))) %>% 
  mutate(item = str_c("FFMQ_", item_number)) %>% 
  select(-item_number) %>% 
  mutate(response = case_when(
    response == "Jamais ou très rarement vrai" ~ 1,
    response == "Rarement vrai" ~ 2,
    response == "Parfois vrai" ~ 3,
    response == "Souvent vrai" ~ 4,
    response == "Très souvent ou toujours vrai" ~ 5,
    TRUE ~ NA_real_
  )) %>% 
  mutate(response = if_else(item %in% c("FFMQ_5", "FFMQ_11", "FFMQ_8", "FFMQ_12", "FFMQ_17", "FFMQ_22", "FFMQ_23", "FFMQ_4", "FFMQ_7", "FFMQ_14", "FFMQ_19", "FFMQ_24"), 6 - response, response)) %>% # Reverse coding
  mutate(sub_scale = case_when(
    item %in% c("FFMQ_6", "FFMQ_10", "FFMQ_15", "FFMQ_20") ~ "FFMQ_Observe",
    item %in% c("FFMQ_1", "FFMQ_2", "FFMQ_5", "FFMQ_11", "FFMQ_16") ~ "FFMQ_Describe",
    item %in% c("FFMQ_8", "FFMQ_12", "FFMQ_17", "FFMQ_22", "FFMQ_23") ~ "FFMQ_Awareness",
    item %in% c("FFMQ_4", "FFMQ_7", "FFMQ_14", "FFMQ_19", "FFMQ_24") ~ "FFMQ_Nonjudgement",
    item %in% c("FFMQ_3", "FFMQ_9", "FFMQ_13", "FFMQ_18", "FFMQ_21") ~ "FFMQ_Nonreactivity"
  ))

tidy_ffmq
```

Jamais ou très rarement vrai = Never or very rarely true Rarement vrai =
Rarely true Parfois vrai = Sometimes true Souvent vrai = Often true Très
souvent ou toujours vrai = Very often or always true

```{r}
tidy_ffmq %>% 
  write_feather("../results/tidy_ffmq.feather")
```

```{r}
ffmq_scales <- tidy_ffmq %>% 
  group_by(ResponseId, sub_scale) %>% 
  summarise(sub_scale_response = sum(response)) %>% 
  filter(!is.na(sub_scale_response)) %>% 
  pivot_wider(ResponseId, names_from = sub_scale, values_from = sub_scale_response) %>% 
  ungroup() %>% 
  mutate(FFMQ_Total = FFMQ_Awareness + FFMQ_Describe + FFMQ_Nonjudgement + FFMQ_Nonreactivity + FFMQ_Observe)
           
ffmq_scales
```

```{r}
ffmq_scales %>% 
  write_feather("../results/ffmq_scales.feather")
```

### ECR

```{r}
tidy_ecr <- df %>% 
  semi_join(ffmq_scales) %>% 
  select(ResponseId, starts_with("ECR")) %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>% 
  mutate(response = as.numeric(str_extract(response, "\\d+$"))) %>% 
  mutate(response = if_else(item %in% c("ECR_6", "ECR_9", "ECR_10", "ECR_11", "ECR_12"), 8 - response, response)) %>%
  mutate(sub_scale = case_when(
    item %in% c("ECR_1", "ECR_2", "ECR_3", "ECR_5", "ECR_7", "ECR_8") ~ "ECR_Anxiety",
    item %in% c("ECR_4", "ECR_6", "ECR_9", "ECR_10", "ECR_11", "ECR_12") ~ "ECR_Avoidance"))

tidy_ecr
```

```{r}
tidy_ecr %>% 
  write_feather("../results/tidy_ecr.feather")
```

```{r}
ecr_scales <- tidy_ecr %>% 
  group_by(ResponseId, sub_scale) %>% 
  summarise(sub_scale_response = sum(response)) %>% 
  filter(!is.na(sub_scale_response)) %>% 
  pivot_wider(ResponseId, names_from = sub_scale, values_from = sub_scale_response) %>% 
  mutate(ECR_Total = ECR_Anxiety + ECR_Avoidance)

ecr_scales
```

```{r}
ecr_scales %>% 
  write_feather("../results/ecr_scales.feather")
```

### DASS

```{r}
tidy_dass <- df %>% 
  semi_join(ffmq_scales) %>% 
  select(ResponseId, starts_with("DASS")) %>% 
  pivot_longer(-ResponseId, names_to = "item", values_to = "response") %>% 
  mutate(response = as.numeric(str_extract(response, "\\d+$"))) %>% 
  mutate(sub_scale = case_when(
    item %in% c("DASS-21_3", "DASS-21_5", "DASS-21_10", "DASS-21_13", "DASS-21_16", "DASS-21_17", "DASS-21_21") ~ "DASS_21_Depression",
    item %in% c("DASS-21_2", "DASS-21_4", "DASS-21_7", "DASS-21_9", "DASS-21_15", "DASS-21_19", "DASS-21_20") ~ "DASS_21_Anxiety",
    item %in% c("DASS-21_1", "DASS-21_6", "DASS-21_8", "DASS-21_11", "DASS-21_12", "DASS-21_14", "DASS-21_18") ~ "DASS_21_Somatization"
))
    
tidy_dass
```

```{r}
tidy_dass %>% 
  write_feather("../results/tidy_dass.feather")
```

```{r}
dass_scales <- tidy_dass %>% 
  group_by(ResponseId, sub_scale) %>% 
  summarise(sub_scale_response = sum(response)) %>% 
  filter(!is.na(sub_scale_response)) %>% 
  pivot_wider(ResponseId, names_from = sub_scale, values_from = sub_scale_response) %>% 
  mutate(DASS_21_Total = DASS_21_Depression + DASS_21_Anxiety + DASS_21_Somatization)

dass_scales
```

```{r}
dass_scales %>% 
  write_feather("../results/dass_scales.feather")
```

```{r}
devtools::session_info()
```
