---
title: "Methods"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(feather)
```

```{r data, include=FALSE}
socs_totals <- read_feather("../results/socs_scales.feather")
demographics <- read_feather("../results/tidy_demographics.feather")
age <- read_feather("../results/age.feather")
gender_summary <- read_feather("../results/gender_summary.feather")
```

## Materials and Methods

A sample of `r count(socs_totals)` French speakers completed an online
survey. Of the `r count(age)` respondents that chose to disclose, the
average age was `r round(mean(age$age), 2)`
(SD=`r round(sd(age$age), 2)`; range:
`r min(age$age)`-`r max(age$age)`). Of the `r sum(gender_summary$count)`
participants that responded,
`r filter(gender_summary, gender == "Féminin")$count` were female,
`r filter(gender_summary, gender == "Masculin")$count` were male, and
`r filter(gender_summary, gender == "Préfère spécifier")$count`
preferred not to specify.
